%% Example CV - Ata Utku Özkan
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Ata Utku Özkan - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Ata Utku}{Özkan}
\address{Ankara, Turkey}{}{}
\email{atautkuozkan@gmail.com}
\extrainfo{\href{https://linkedin.com/in/ata-utku-ozkan}{LinkedIn}, \href{https://github.com/Ata-gith}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{PhD computational physicist (Bilkent UNAM, exp. 2026) with 6+ years of molecular simulation spanning the full scale ladder: classical MD, ab-initio MD, DFT, and TDDFT (LAMMPS, GROMACS, VASP, Quantum Espresso, DeePMD). First author of a JPCB 2023 paper and a manuscript under review in Physical Review Materials; second author of a bioRxiv 2026 preprint. Production-grade Python developer across cheminformatics (RDKit, molecular docking, QSAR/ADMET) and statistical/stochastic modelling (Bayesian inference, Gaussian processes, MCMC). Transitioning from academic research to an industry research scientist role in computational chemistry/drug design or quantitative research.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Molecular Simulation}: LAMMPS, GROMACS, OpenMM, NAMD; enhanced sampling (replica exchange, umbrella sampling, metadynamics); free-energy methods (FEP, thermodynamic integration)

\item \textbf{Ab-initio \& Electronic Structure}: DFT and TDDFT (VASP, Quantum Espresso, ORCA); machine-learned potentials (DeePMD); ionic transport in 2D materials

\item \textbf{Cheminformatics \& Drug Design}: RDKit, molecular docking (AutoDock Vina, GNINA), QSAR/ADMET modelling, graph neural networks for structure-property prediction

\item \textbf{Statistical \& Stochastic Modelling}: Bayesian inference, Gaussian processes, ELBO/variational optimization, MCMC, stochastic differential equations, time-series (ARMA/GARCH)

\item \textbf{Programming \& HPC}: Python (NumPy, SciPy, pandas, PyTorch, scikit-learn), C/C++ (MPI), SLURM/HPC automation

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- PhD Researcher ---
\item{\cventry{2022--Present}{PhD Researcher}{Bilkent University, UNAM}{Ankara, Turkey}{}{\vspace{1pt}
\begin{itemize}
    \item Ran 100+ all-atom non-equilibrium MD simulations (LAMMPS, up to 100 ns each) on national HPC to resolve the microscopic origin of anomalous ionic conductivity in Na$^+$-intercalated layered MnO$_2$
    \item Demonstrated a collective ionic conduction regime that violates the Nernst--Einstein relation; decoupled morphology from hydration effects via frozen-layer control simulations
    \item Built the end-to-end Python analysis pipeline (NumPy, pandas, SciPy, NetworkX, OVITO) for a coarse-grained MD study of nuclear lamina self-assembly (1250-chain system, 22{,}500-bead elastic shell)
    \item First author, manuscript under review, \textit{Physical Review Materials}; second author, bioRxiv 2026 preprint
\end{itemize}}}

\vspace{3pt}

% --- MS Researcher ---
\item{\cventry{2019--2022}{MS Researcher}{Bilkent University, UNAM}{Ankara, Turkey}{}{\vspace{1pt}
\begin{itemize}
    \item First-author study (JPCB 2023): all-atom MD (GROMACS) across seven protonation states showing pH-driven conformational switching kinetics of [5]rotaxane, validated across 20 replicas and two independent force fields
    \item Simulated polyrotaxane 2D network formation at a water--chloroform interface; characterised network porosity and charge-state-dependent lateral expansion
\end{itemize}}}

\vspace{3pt}

% --- Computational Risk Analysis Intern ---
\item{\cventry{Mar--Jun 2017}{Computational Risk Analysis Intern}{Nurol Makine ve Sanayi A.Ş.}{Ankara, Turkey}{}{\vspace{1pt}
\begin{itemize}
    \item Statistical forecasting and computational risk modelling in the quality control department
\end{itemize}}}

\vspace{3pt}

% --- Research Intern ---
\item{\cventry{Jan--Mar 2017}{Research Intern}{METU Nanomagnetics Instruments}{Ankara, Turkey}{}{\vspace{1pt}
\begin{itemize}
    \item Atomic force microscopy calibration and imaging (AFM, PFM/MFM, Aqua AFM); quantitative surface analysis
\end{itemize}}}

\vspace{3pt}

% --- Engineering Intern ---
\item{\cventry{Jan--Mar 2016}{Engineering Intern}{Aydöküm A.Ş.}{Ankara, Turkey}{}{\vspace{1pt}
\begin{itemize}
    \item Continuum mechanics simulation and microstructure phase data analysis for cast iron products
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2022--Present}{PhD, Materials Science and Nanotechnology}{Bilkent University (UNAM)}{Ankara, Turkey}{}{\vspace{1pt}
Dissertation: ``Molecular Dynamics Study of Ionic Transport and Self-Assembly in Soft and 2D Materials.'' Expected completion 2026.
}}

\vspace{3pt}

\item{\cventry{2019--2022}{M.Sc., Materials Science and Nanotechnology}{Bilkent University (UNAM)}{Ankara, Turkey}{}{\vspace{1pt}
Thesis: ``Molecular Dynamics Simulations Study of Rotaxane in Bulk and at Interfaces.''
}}

\vspace{3pt}

\item{\cventry{2014--2019}{B.S., Materials Science and Nanotechnology Engineering}{TOBB ETÜ}{Ankara, Turkey}{}{\vspace{1pt}
Thesis: ``Computational Modeling of Peptide--Graphene Interactions.''
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Turkish (native), English (advanced/full professional), German (A2), French (A2).
\end{itemize}

% ============================================================
%     PUBLICATIONS (optional)
% ============================================================

\section{Publications}
\vspace{1pt}
\begin{itemize}
\item A. U. Özkan, D. Tuncel, A. Erbaş (2023). Effect of charge state on the equilibrium and kinetic properties of mechanically interlocked [5]Rotaxane: A molecular dynamics study. \textit{The Journal of Physical Chemistry B}, 127(5), 1254--1263. \href{https://doi.org/10.1021/acs.jpcb.2c07645}{DOI link}
\item A. U. Özkan, T. S. Kasırga, A. Erbaş (2026). Ionic transport in spontaneously ion-intercalated van der Waals layered structures. Manuscript under review, \textit{Physical Review Materials}. \href{https://arxiv.org/abs/2601.14836}{arXiv:2601.14836}
\item H. A. Hameed, A. U. Ozkan, A. Erbas (2026). Inter-lamin interactions control meshwork topology in a polymer-gel model of nuclear lamina. \textit{bioRxiv} preprint. \href{https://doi.org/10.64898/2026.03.14.711786}{DOI link}
\end{itemize}

% ============================================================
%     HONORS AND AWARDS (optional)
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{TÜBİTAK 2211-C} -- National PhD Scholarship in Priority Fields in Science and Technology (2025).}
\item{\textbf{TÜBİTAK 2224-A} -- Grant for Participation in Scientific Meetings Abroad (2024).}
\item{\textbf{TÜBİTAK 2250} -- Performance-Based Scholarship for PhD Scholars (2024).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
